Title

### 2013-02-23 inc/model_results/lens_charge/lens_charge.tex
improve lens_charge section

\begin{figure}
  \centering
  \subfloat[][] {
    \label{fig:focus_lens_charge_long}
    \input{lens_60mm}
  }
  \\
  \subfloat[][] { 
    \label{fig:focus_lens_charge_short}
    \input{lens_6mm}
  }
  \caption{ PLACEHOLDER
  %Focal behavior of perfect magnetic lenses predicted by the AG model (with DC acceleration voltage of 20kV) as a function of pulse charge $N$: \subref{fig:LongPancake} $f = $ 63.5mm and disk-like ($ w = 500 \mu \text{m}$ and $ \xi ( 0 ) = 0.1 $); \subref{fig:LongCigar} $ f = $ 63.5mm and cigar-like ($ w = 107.7 \mu \text{m}$ and $ \xi ( 0 ) = 10 $); \subref{fig:ShortPancake} $ f = $ 6.35mm and disk-like ($ w = 500 \mu \text{m}$ and $ \xi ( 0 ) = 0.1 $); \subref{fig:ShortCigar} $ f = $ 6.35mm and cigar-like ($ w = 107.7 \mu \text{m}$ and $ \xi ( 0 ) = 10 $). A logarithmic scale is used for comparative clarity.
  }
  \label{fig:focus_lens_charge}
\end{figure}

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for prolate pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_long}) and a `short' focal length of 6.0mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_short}).
%In all cases, the pulse is assumed to be accelerated to 20kV and generated from a Ta photocathode with a negligible excess photoemission energy (i.e., $ \eta_{i} \rightarrow 0 $) in order to highlight the effect of space-charge. For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased. The single-electron ($ N = 1 $) focal spot sizes of $\sim$6 microns for the $ f = 63.5 \text{mm} $ lens and $\sim$0.6 microns for the shorter $ f = 6.35 \text{mm} $ lens increase markedly for $ N \gtrsim 10^{ 5 } $ and $ N \gtrsim 10^{ 6 }$, respectively. This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 63.5\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing. A consequent further effect is a shift in the focal position to $ z > f $.  A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\Fig \ref{fig:compare}). Thus, the electron pulse propagation model predicts that higher fidelity focusing will be achieved with shorter focal length magnetic lenses, higher acceleration energy electrons (time of flight reduction), and pulses with $ \sigma_{ \smallT } \gg \sigma_{ z } $ at the entrance aperture of the lens.

>>>>

\begin{figure}
  \centering
  \subfloat[][] {
    \label{fig:focus_lens_charge_long}
    \input{lens_60mm}
  }
  \\
  \subfloat[][] { 
    \label{fig:focus_lens_charge_short}
    \input{lens_6mm}
  }
  \caption[AG model simulated focal behavior of perfect magnetic lenses as a function of pulse charge $N$]{
    Focal behavior of perfect magnetic lenses predicted by the AG model (with DC acceleration voltage of 20kV) as a function of pulse charge $N$.
    Pulses begin at the lens' front focal plane with HW1/eM width $ 500 \mu \text{m}$ and duration 500 fs at 20 kV velocity ($c/3$) or ellipticiy $ \xi ( 0 ) = 0.1 $ (prolate).
    Distance traveled in column is measured relative to the lens at $z=0$, in units of the focal lenth, \subref{fig:focus_lens_charge_long} $f = $ 60mm and \subref{fig:focus_lens_charge_short} $ f = $ 6.35mm.
    A logarithmic scale is used for comparative clarity.
  }
  \label{fig:focus_lens_charge}
\end{figure}

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for prolate pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_long}) and a `short' focal length of 6.0mm (\ref{fig:focus_lens_charge}\subref{fig:focus_lens_charge_short}).
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
The length of the accelerator and the anode lensing would make useful comparison difficult; as such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

The single-electron ($ N = 1 $) focal spot sizes of $\sim$150 microns for the $ f = 60 \text{mm} $ lens and $\sim$15 microns for the shorter $ f = 6.0 \text{mm} $ lens show marked increase starting around $ N \approx 10^{ 5 } $ and $ N \approx 10^{ 6 }$, respectively, and worsening dramatically above these thresholds.
This order of magnitude difference is fundamentally related to the greater time of flight before the focus of the $ f = 60\text{mm} $ lens; it increases the impulse that the internal Coulomb force can exert on the pulse as its charge density is increased under focusing.
A consequent further effect is a shift in the focal position to $ z > f $.
%A more subtle effect is that disk-like pulses are more readily focused than cigar-like pulses --- the rate of transverse pulse broadening due to space-charge effects already being intrinsically greater in the latter (\Fig \ref{fig:compare}). Thus, the electron pulse propagation model predicts that higher fidelity focusing will be achieved with shorter focal length magnetic lenses, higher acceleration energy electrons (time of flight reduction), and pulses with $ \sigma_{ \smallT } \gg \sigma_{ z } $ at the entrance aperture of the lens.
